\subsection{UVa11286 - Comformity}
Frosh commencing their studies at Waterloo have diverse interests, as evidenced by their desire to take various combinations of courses from among those avaliable.

University administrators are uncomfortable with this situation, and therefore wish to offer a \textit{comformity prize} to frosh who choose the most popular combination of courses. How many frosh will win the prize?

\begin{flushleft}
{\color{red} \textbf{Input}}
\end{flushleft}
The input consists of several test cases followed by a line containing '$0$'. Each test case begins with as integer $1 \leq n \leq 10000$, the number of frosh. For each frosh, a line follows containing the course numbers of five distinct courses selected by the frosh. Each course number is an integer between $100$ and $499$.

The \textit{popularity} of a combination is the number of frosh selecting exactly the same conbination of courses. A conbination of courses is considered \textit{most popular} if no other combination has higher popularity.

\begin{flushleft}
{\color{red} \textbf{Output}}
\end{flushleft}
For each line of input, you should output a single line giving the total number of students taking some combination of courses that is most popular.

\begin{flushleft}
{\color{red} \textbf{Sample Input}}
\end{flushleft}
\begin{flushleft}
3\\
100 101 102 103 488\\
100 200 300 101 102\\
103 102 101 488 100\\
3\\
200 202 204 206 208\\
123 234 345 456 321\\
100 200 300 400 444\\
0\\
\end{flushleft}

\begin{flushleft}
{\color{red} \textbf{Sample Output}}
\end{flushleft}
\begin{flushleft}
2\\
3\\
\end{flushleft}

\newpage